Meta-analysis

### 2019-11-13 02_Weather.Rmd

```{r import_libraries_&_data}
source("R/import_data.R")
PM.dat <- import_data()  # importing means yield and disease severity for each treatment within each powdery mildew trial on mungbean
source("R/year2day.r")

>>>>

```{r import_libraries_&_data}
library(ggplot2)
source("R/import_data.R")
PM.dat <- import_data()  # importing means yield and disease severity for each treatment within each powdery mildew trial on mungbean
source("R/year2day.r")
